\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-19 notes/2loopNLSM.tex
A very rough first abstract.

  We catalog and analyze ?4? theories which all manifest the duality
  between color and kinematics both at tree and one-loop level.  We
  identify a unifying theory, \emph{semi-abelian} Yang--Mills, from
  which all four of the theories can be extracted.  Joint
  consideration of these theories sheds light on the long-standing
  problem.

  \begin{itemize}
  \item Catalog themes among ``manifestly'' color dual theories
  \item Identify obstructions going $1 \to 2$ loop
  \item Highlight obstructions and overcome via NLSM bootstrap
  \item Brief revisit of 2L YM
  \end{itemize}

>>>>

  We catalog and analyze ?4? theories which all manifest the duality
  between color and kinematics both at tree and one-loop level.  We
  identify a unifying theory, \emph{semi-abelian} Yang--Mills, from
  which all four of the theories can be extracted.  Joint
  consideration of these theories highlights that the lifting of
  one-loop color-kinematics dual numerators to two loops may be just
  as challenging as the step from tree level to one loop.  As a first
  step in understanding the two-loop challenge, we construct
  color-dual two-loop four-point non-linear sigma model (NLSM)
  numerators using generalized unitarity methods.  The double-copy of
  the constructed NLSM numerators with themselves, $\mathcal{N}=0$
  Yang--Mills, and $\mathcal{N}=4$ Yang--Mills correctly reproduce the
  known physical unitarity cuts of special Gallileons, Born-Infeld
  theory, and Dirac-Born-Infeld-Volkov-Akulov theory, respectively.
  These NLSM numerators are in explicit tension with generalizations
  of the one-loop NLSM numerators. \ace{I realize that we all know
    this, but does/will a statement to this effect actually make it
    into the draft?}  Additionally, we revisit the two-loop four-point
  Yang--Mills problem in order to identify the exact point of
  inconsistency in a local color-dual construction.
